\documentclass[../dissertation.tex]{subfiles}

\begin{document}

\textit{Several sections that reflect on your experiences during the team project. Each section should discuss one theme, characterised by incidents or events that occurred during the team course of the project from which you learned (approximately 8-10 pages).}

Reflecting on your practice is the hardest part of writing the dissertation, so you are encouraged to talk to the course coordinators and demonstrators to find out what you could include in this section. A good source of examples of incidents for reflection is often the documentation from your retrospectives, because you used the retrospectives to identify areas of your process that could be changed or done better. You should also, try to relate your experiences to other studies available in the software engineering literature (the recommended reading is a good starting point for this). For example, if you found that you had to drop a feature during an iteration, discuss the reasons why the feature had to be dropped. Had you given yourselves too much work? Was the feature harder to implement than you realised? Had you got your priorities wrong? Then consider looking at the literature (see the recommended reading for PSD3) on project planning and estimation. Was your experience typical of a software project? What steps do other developers advocate for improving estimation? Alternatively, did you have to make some big design decisions or choice of software platforms early on in the project? What impact did these choices have? Were they the right ones? How might you have improved the decision making process to reduce uncertainty? Did you implement a prototype before proceeding to far with the main implementation? How much effort did this involve? What did you learn about the platform as a result?

\subsection{The Plan}

\textit{What was the initial course of action? How was the plan documented and was it realistic?}

\subsection{Features}

\textit{What were the key features of the product?}

\subsection{Refining the Product}

\textit{How were requirements refined with the customer? What changes had to be made to the application?}

\subsection{The Final Product}

\textit{How was the final product delivered?}

\subsection{Deployment}

\textit{How has the application been deployed?}

\end{document}
