\documentclass[../dissertation.tex]{subfiles}

\begin{document}

This paper presents a case study of ``UniCom - The Student Feedback Application", a project that was developed for the third year Computer Science Team Project course. The team - ESE01 - consisted of 4 Electronic and Software Engineering students at the University of Glasgow.

The project customer was Dr Mark Wong, who requested an application to be developed to improve the student learning experience and to create a new platform for giving and receiving feedback in the Social and Public Policy undergraduate program at our university.

This dissertation explains the team's development effort as we developed this application. This includes challenges that were faced during the process as well as significant achievements that were made.

In particular, it will demonstrate how the team used Agile software development to undertake this project, as well as how other software engineering practices that were taught in Professional Software Development 3 were applied during the process.


The rest of the case study is structured as follows:

We present a case study which describes the project customer and context, as well as objectives and project state at the time of writing. This is covered in \nameref{case_study}.

Next we cover the development effort itself, including a number of issues that arose during the project and how they were overcome. This is covered in \nameref{development}.

The technologies used in the project are then discussed in \nameref{technologies}, including explanations for why these technologies were used and how they were applied.

A key aspect of the development effort was the use of GitLab to maintain high quality documentation and testing of code. This is covered in \nameref{software_process}.

Working well in a team is fundamental to the successful development of a project. In \nameref{teamwork} we discuss how the team assigned roles to different members, as well as challenges that were faced with Agile development.

INCLUDE SOMETHING IN SECTION 7 ?

Finally, we present our conclusions of the project, including the entire process and future steps that can be taken for the application in \nameref{conclusions}.

\end{document}
