\documentclass[../dissertation.tex]{subfiles}

\begin{document}

\subsection{GitLab}

\textit{How was git used for version control?}

\textit{What was the procedure to develop new features? (Issue, branch, code review, merge request)}

\subsubsection{Issues}

\textit{How were issues used? Where they useful? How were tickets used?}

\textit{Were new tasks created as the team discovered new tasks?}

\textit{Was task meta data documented? (priority, estimates etc)}

\subsubsection{Branches}

\textit{How was the branch made to ensure easy understanding of which issue it related to? Did members push often?}

\subsubsection{Commits}

\textit{Where commit messages written well? Where there regular commits?}

\subsubsection{Merge Requests}

\textit{What was the procedure for merge requests? (Template -> code review -> comment -> merge)}

\subsection{Quality Assurance}

\subsubsection{Testing}

\textit{Did the team have an automated test suite for regression testing purposes? Did the test suite provided effective coverage of the project?}

\subsubsection{Continuous Integration}

\textit{Was every commit tested in a continuous integration environment? Did the team immediately fix any broken builds report by the CI environment?  Did the team perform code reviews (evidence from wiki or commit messages?)}

\subsection{Iterations and Retrospectives}

\textit{Did the team hold regular post-iteration retrospectives? Were the retrospectives used effectively to (a) identify problems and (b) identify practical solutions? Were the results of the retrospectives documented? Were the solutions implemented? Was the effectiveness of a solution evaluated?}

\end{document}
